---
title: "PSResearchDesign_Systems"
author: "Adrian Brenner 12422308"
date: "2024-03-03"
output: 
  pdf_document:
    toc: false
    number_sections: false
    latex_engine: pdflatex
header-includes:
  - \usepackage{float}
---


This file is part of the PS Research Design Term Paper of Adrian Brenner.

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(dplyr)
opts_chunk$set(echo=FALSE)
```

**On the weather day classification:**
```{r}
# Load readxl package
library(readxl)

data <- read_excel("C:/Users/AD/Desktop/HA_PS/WETTER BEREINIGT.xlsx")
```

```{r}
# Exclude the first 3 rows and select the 'Mittel' column
mittel_column <- data$Mittel[-(1:3)]

# Coerce values to numeric
mittel_column <- as.numeric(as.character(mittel_column))

# Calculate the sum of the 'Mittel' column
sum_mittel <- sum(mittel_column, na.rm = TRUE)

# Calculate the arithmetic mean
mean_mittel <- mean(mittel_column, na.rm = TRUE)
```


```{r}
# Exclude the first 3 rows and select the 'Nieder-' column
nieder_column <- data$`Nieder-`[-(1:3)] # Using backticks to handle column name with special characters

# Coerce values to numeric
nieder_column <- as.numeric(as.character(nieder_column))

# Calculate the sum of the 'Nieder-' column
sum_nieder <- sum(nieder_column, na.rm = TRUE)

# Calculate the arithmetic mean
mean_nieder <- mean(nieder_column, na.rm = TRUE)
```



```{r}
# Exclude the first 3 rows and select the 'Sonne-' column
sonne_column <- data$`Sonnen-`[-(1:3)] # Using backticks to handle column name with special characters
 
# Coerce values to numeric
sonne_column <- as.numeric(as.character(sonne_column))

# Calculate the sum of the 'Sonne-' column
sum_sonne <- sum(sonne_column, na.rm = TRUE)

# Calculate the arithmetic mean
mean_sonne <- mean(sonne_column, na.rm = TRUE)
```

Mean of Temperature: 11.05

11.05 * 1.4 = 15.47
11.05 * 1.3 = 14.365
11.05 * 0.7 = 7.735
11.05 * 0.6 = 6.63

Mean of Precipitation: 3.20

3.20 * 1.4 = 4.48
3.20 * 1.3 = 4.16
3.20 * 0.7 = 2.24
3.20 * 0.6 = 1.92

Mean of Sunshine hours: 5.38

5.38 * 1.4 = 7.532
5.38 * 1.3 = 6.994
5.38 * 0.7 = 3.766
5.38 * 0.6 = 3.228

Obviously there are a lot of strong outlying days in the Sunshine and Rainfall factor, that could present their mean score to be misleading, here it would be possible to opt for a Median approach as well. I did not decide for that, as I choose mean calculations for all other factors as well, consequently a deviation would be more unjust than just in this papers case. A practical mean deficit should become visible with a low amount of "average" sunshine and precipitation classified days.


**Temperature Treatment Classification**

```{r}
# Extract the 'Mittel' column starting from row 4 and convert to numeric
mittel_column <- as.numeric(as.character(data$Mittel[4:26]))

# Define the break points for the categories
breaks <- c(-Inf, 6.63, 7.735, 14.365, 15.47, Inf)

# Define the labels for the categories
labels <- c("Under 6.63", "Between 6.63 and 7.735", "Between 7.735 and 14.365", "Between 14.365 and 15.47", "Over 15.47")

# Cut the 'Mittel' column into categories
mittel_categories <- cut(mittel_column, breaks = breaks, labels = labels, include.lowest = TRUE)

# Display the frequency of each category
table(mittel_categories)
```


```{r}
# Extract the 'Mittel' column starting from row 27 and convert to numeric
mittel_column <- as.numeric(as.character(data$Mittel[27:45]))

# Define the break points for the categories
breaks <- c(-Inf, 6.63, 7.735, 14.365, 15.47, Inf)

# Define the labels for the categories
labels <- c("Under 6.63", "Between 6.63 and 7.735", "Between 7.735 and 14.365", "Between 14.365 and 15.47", "Over 15.47")

# Cut the 'Mittel' column into categories
mittel_categories <- cut(mittel_column, breaks = breaks, labels = labels, include.lowest = TRUE)

# Display the frequency of each category
table(mittel_categories)
```
```{r}
# Extract the 'Mittel' column starting from row 46 and convert to numeric
mittel_column <- as.numeric(as.character(data$Mittel[46:64]))

# Define the break points for the categories
breaks <- c(-Inf, 6.63, 7.735, 14.365, 15.47, Inf)

# Define the labels for the categories
labels <- c("Under 6.63", "Between 6.63 and 7.735", "Between 7.735 and 14.365", "Between 14.365 and 15.47", "Over 15.47")

# Cut the 'Mittel' column into categories
mittel_categories <- cut(mittel_column, breaks = breaks, labels = labels, include.lowest = TRUE)

# Display the frequency of each category
table(mittel_categories)
```

For Pre-Treatment Temperature:
9 bad weather
5 below average
8 average
1 above average
0 good weather

For Treatment Temperature:
0 bad weather
2 below average
13 average
2 above average
2 good weather

For Post-Treatment Temperature:
0 bad weather
0 below average
8 average
1 above average
10 good weather

Clear positive skewness for temperature as time goes on

**Precipitation Treatment Classification**

```{r}
# Extract the 'Nieder-' column starting from row 4 and convert to numeric
nieder_column <- as.numeric(as.character(data$`Nieder-`[4:26]))

# Define the break points for the categories
breaks <- c(-Inf, 1.92, 2.24, 4.16, 4.48, Inf)

# Define the labels for the categories
labels <- c("Under 1.92", "Between 1.92 and 2.24", "Between 2.24 and 4.16", "Between 4.16 and 4.48", "Over 4.48")

# Cut the 'Nieder-' column into categories
nieder_categories <- cut(nieder_column, breaks = breaks, labels = labels, include.lowest = TRUE)

# Display the frequency of each category
table(nieder_categories)
```
```{r}
# Extract the 'Nieder-' column starting from row 27 and convert to numeric
nieder_column <- as.numeric(as.character(data$`Nieder-`[27:45]))

# Define the break points for the categories
breaks <- c(-Inf, 1.92, 2.24, 4.16, 4.48, Inf)

# Define the labels for the categories
labels <- c("Under 1.92", "Between 1.92 and 2.24", "Between 2.24 and 4.16", "Between 4.16 and 4.48", "Over 4.48")

# Cut the 'Nieder-' column into categories
nieder_categories <- cut(nieder_column, breaks = breaks, labels = labels, include.lowest = TRUE)

# Display the frequency of each category
table(nieder_categories)
```
```{r}
# Extract the 'Nieder-' column starting from row 46 and convert to numeric
nieder_column <- as.numeric(as.character(data$`Nieder-`[46:64]))

# Define the break points for the categories
breaks <- c(-Inf, 1.92, 2.24, 4.16, 4.48, Inf)

# Define the labels for the categories
labels <- c("Under 1.92", "Between 1.92 and 2.24", "Between 2.24 and 4.16", "Between 4.16 and 4.48", "Over 4.48")

# Cut the 'Nieder-' column into categories
nieder_categories <- cut(nieder_column, breaks = breaks, labels = labels, include.lowest = TRUE)

# Display the frequency of each category
table(nieder_categories)
```
For Pre-Treatment Precipitation:
5 bad weather
0 below average
3 average
0 above average
15 good weather

For Treatment Precipitation:
7 bad weather
0 below average
2 average
0 above average
10 good weather

For Post-Treatment Precipitation:
1 bad weather
0 below average
0 average
0 above average
18 good weather

**Sunshine Treatment Classification**

```{r}
# Extract the 'Sonnen-' column starting from row 4 and convert to numeric
sonnen_column <- as.numeric(as.character(data$`Sonnen-`[4:26]))

# Define the break points for the categories
breaks <- c(-Inf, 3.228, 3.766, 6.994, 7.532, Inf)

# Define the labels for the categories
labels <- c("Under 3.228", "Between 3.228 and 3.766", "Between 3.766 and 6.994", "Between 6.994 and 7.532", "Over 7.532")

# Cut the 'Sonnen-' column into categories
sonnen_categories <- cut(sonnen_column, breaks = breaks, labels = labels, include.lowest = TRUE)

# Display the frequency of each category
table(sonnen_categories)
```
```{r}
# Extract the 'Sonnen-' column starting from row 27 and convert to numeric
sonnen_column <- as.numeric(as.character(data$`Sonnen-`[27:45]))

# Define the break points for the categories
breaks <- c(-Inf, 3.228, 3.766, 6.994, 7.532, Inf)

# Define the labels for the categories
labels <- c("Under 3.228", "Between 3.228 and 3.766", "Between 3.766 and 6.994", "Between 6.994 and 7.532", "Over 7.532")

# Cut the 'Sonnen-' column into categories
sonnen_categories <- cut(sonnen_column, breaks = breaks, labels = labels, include.lowest = TRUE)

# Display the frequency of each category
table(sonnen_categories)
```
```{r}
# Extract the 'Sonnen-' column starting from row 46 and convert to numeric
sonnen_column <- as.numeric(as.character(data$`Sonnen-`[46:64]))

# Define the break points for the categories
breaks <- c(-Inf, 3.228, 3.766, 6.994, 7.532, Inf)

# Define the labels for the categories
labels <- c("Under 3.228", "Between 3.228 and 3.766", "Between 3.766 and 6.994", "Between 6.994 and 7.532", "Over 7.532")

# Cut the 'Sonnen-' column into categories
sonnen_categories <- cut(sonnen_column, breaks = breaks, labels = labels, include.lowest = TRUE)

# Display the frequency of each category
table(sonnen_categories)
```
For Pre-Treatment Sunshine:
16 bad weather
0 below average
0 average
0 above average
7 good weather

For Treatment Sunshine:
7 bad weather
0 below average
7 average
0 above average
5 good weather

For Post-Treatment Sunshine:
6 bad weather
0 below average
5 average
0 above average
8 good weather

**Cumulative Weather Classsification**


Here I just cross reference alll results and look how many days are true for at least 2 out of 3 variables (Temperature, Precipitation, Sunshine).

For Pre-Treatment:
9 bad weather
0 below average
3 average
0 above average
7 good weather

For Treatment:
6 bad weather
0 below average
7 average
0 above average
5 good weather

For Post-Treatment:
6 bad weather
0 below average
5 average
0 above average
10 good weather

It becomes obvious, that the threshold of the classified above and below average weather is not efficiently chosen, as it is to slim to actually encapsulate any instances of 2 our of 3 variables fitting. A lower threshold of 15% might me much more suitable, or even a raise of the good and bad classifications to 50%. Anything that raises the slim 10% margin window will help to make those classifications more efficent, as per this papers classification they are unused.

**On the calculation of children per family household:**

52.8% of household have 1 child.

36.3% have 2.

8.1% have 3.

2.7% 4 or more, so here I use 4.2 as a proposed calulation number. (As most of those household most likely have 4 children.)

As per p.6 of Landeshauptstadt Bayern: https://stadt.muenchen.de/dam/jcr:d84c2a4e-6bfb-453b-8951-65aae1da174a/Kurzinformation_Familien_in_Muenchen_181012.pdf

```{r}
0.528 * 1 + 0.363 * 2 + 0.081 * 3 + 0.027 * 4.2 
```
So a rough average of 1.6 children per family household.

**DID Model Calculation**
-> Done with inline Math directly in LaTeX.

Adrian Brenner (12422308) for GSI LMU - PS Research Design (15441) - Prof. Dr. Alexander Wuttke
